 Group Report

### 2024-12-09 draft.Rmd
Update draft.Rmd

From this model, we got an adjusted $R^2$ value of 0.289, meaning that
our model explains 28.9% of the variance in log of (G1_G2_Average).
Additionally, this adjusted $R^2$ value did improve by 4.6%, however the
$R^2$ value our model achieve is not that high indicating that the
relationship between target and predictor might not have a log-linear
relationship between them.

@@

The summary of our model shows that all four variables are statistically
significant at a critical value of 0.05, indicating to us that these
four variables have a meaningful relationship with G1_G2_Average.
Specifically, \* schoolMS has a negative correlation with
log(G1_G2_Average) with estimate -1.54. This implies that being in
school MS (Mousinho da Silveira) as compared to school GP (Gabriel
Pereira) is associated with a decrease in log(G1_G2_Average) by 1.54
when other variables are constant \* Medu has a positive correlation of
0.257, implying that for a unit increase in Mother's educational level,
the log(G1_G2_Average) increases by 0.257 units. \* higherYes has a
positive correlation of 2.47, implying that an increase in 2.47 units in
log(G1_G2_Average) is observed for students planning to pursue a degree
compared to those who are not interested. \* absences has a negative
correlation of 0.108, implying that every additional day of absences is
associated with a decrease in log(G1_G2_Average) by 0.108 units.

>>>>

From this model, we got an $R^2$ value of 0.259, meaning that our model 
explains 25.9% of the variance in log of (G1_G2_Average). Additionally, 
this $R^2$ value did not improve, and the $R^2$ value our model achieve 
is not that high indicating that the relationship between target and 
predictor might not have a log-linear relationship between them.

@@

The summary of our model shows that all four variables are statistically
significant at a critical value of 0.05, indicating to us that these
four variables have a meaningful relationship with G1_G2_Average.
Specifically, \* schoolMS has a negative correlation with
log(G1_G2_Average) with estimate -1.42. This implies that being in
school MS (Mousinho da Silveira) as compared to school GP (Gabriel
Pereira) is associated with a decrease in log(G1_G2_Average) by 1.42
when other variables are constant \* Medu has a positive correlation of
0.215, implying that for a unit increase in Mother's educational level,
the log(G1_G2_Average) increases by 0.215 units. \* higherYes has a
positive correlation of 2.41, implying that an increase in 2.41 units in
log(G1_G2_Average) is observed for students planning to pursue a degree
compared to those who are not interested. \* absences has a negative
correlation of 0.131, implying that every additional day of absences is
associated with a decrease in log(G1_G2_Average) by 0.131 units.
